%configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Melvyn Ian }{Drag}
\address{416 Plymouth Rd. North Brunswick, NJ 08902}
\mobile{(201) 443 7660} 
%%% Social
\email{melvyniandrag@gmail.com}
\homepage{www.melvyniandrag@github.io}
\github{melvyniandrag}
%%% Optionals
\position{Computer Scientist{\enskip\cdotp\enskip}Machine Learning Engineer{\enskip\cdotp\enskip}Optimization Expert}
\quote{"There are few things in life more interesting than computing" - The Little Schemer by Felleisen and Freidman}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Computer Science Dept.}
  {NJCU\\2039 John F. Kennedy Blvd\\ Jersey City, NJ 07305}
\letterdate{\today}
\lettertitle{Computer Science Adjunct Application}
\letteropening{Dear Sir or Madam,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Melvyn Ian Drag~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}
\cvparagraph{About Me}
I create computational solutions to hard problems, ranging from diffusion to predictive analytics, and beyond. I love Python, C++, and CUDA, and I am a big proponent of functional programming. I'm also fascinated by the way that computers work, and I have engineer-level knowledge of how processors process, assembly assembles, and memory memorizes.

\cvparagraph{Why NJCU?}
NJCU is my alma mater, and I'd like to contribute to its rise as a top-notch university. "There are few things in life more interesting than computing", and I'd like to work with young people to help them understand why this is true. There is a lot of potential for greatness in NJCU students, and I'd like to help students achieve this greatness.

\cvparagraph{Why Me?}
I write complex software. I have a deep knowledge of data structures and algorithms. I can teach version control and coding style.  I'm very active ``in the scene"\footnote{I'm writing to you from the ODSC conference in Boston, and I'll be presenting at the Central NJ Data Science group in June, and at PyGotham in NYC in July. I contribute to open source projects.}, can help your students see what it is to be a programmer, and can help them find employment. In short, I would be a \textbf{no-nonsense professor} with lots of truth and inspiration for your students.
\cvparagraph{What's Next?}
At my current job I regularly interview prospective software engineers. I ask them questions like:
\begin{enumerate}
\item How would you implement a function that takes $x$, $y$, $z$ as input and returns $a$ as output?
\item What is the complexity of the \textit{foobarbaz} algorithm?
\item Can you explain what \textit{state} refers to in the concept of computer programming?
\end{enumerate}
I would be honored if you would have me in to ask me similar questions (and potentially offer me a job)!

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}

