\documentclass[]{deedy-resume-openfont}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Melvyn}{Drag}{ Nature and Technology Lover. Future Robotic Celestial Navigation Programmer. \\
\href{mailto:melvyniandrag@gmail.com}{melvyniandrag@gmail.com} | 603.724.1451
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     EDUCATION
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Education} 

    \subsection{Ohio State University}
    \descript{Master of Mathematical Science}
    \location{2013-2015 | Columbus, OH}
    Specialty in Computational Science \\
    Full Scholarship + Grants
    \sectionsep

    \subsection{ NJCU }
    \descript{BA in Mathematics}
    \location{2012 | Jersey City, NJ}
    Math, Science, Linguistics.\\
    Full Scholarship
    \sectionsep

    \subsection{Bayonne High School }
    \location{2006 |  Bayonne, NJ }
    AP, Honors Everything\\
    \sectionsep

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     LINKS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Links} 
    Github:// \href{https://github.com/melvyniandrag}{\custombold{melvyniandrag}} \\
    LinkedIn://  \href{https://www.linkedin.com/in/melvyn-ian-drag-374613107/}{\custombold{melvyn-ian-drag}} \\
    YouTube://  \href{https://www.youtube.com/results?search_query=Melvyn+Drag}{\custombold{Melvyn Drag}} \\
    Blog://  \href{https://www.melvyniandrag.github.io}{\custombold{melvyniandrag}} \\
    Instructables:// \href{https://www.instructables.com/member/MelvynD/}{\custombold{MelvynD}}
    \sectionsep

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     COURSEWORK
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Coursework}
    \subsection{Graduate}
    Advanced Algorithms \\
    Parallel Computing \\
    Numerical PDEs \\
    Computational Geometry \\
    Analytical PDEs \\ 
    Biological Simulation
    \sectionsep

    \subsection{Undergraduate}
    Differential Equations \\
    Statistics \\
    Linear Algebra \\
    Etc.
    \sectionsep

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     SKILLS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Skills}
    \subsection{Programming}
    \location{I Love Working With}
    C++ \textbullet{}   Python \textbullet{} Vim \textbullet{} Linux \textbullet{} Bluetooth \textbullet{} Docker \textbullet{} Godot Game Engine \\
    I've learned alot of other stuff along the way, too.
    \sectionsep

    \section{Talks}
    \subsection{PyOhio 2014}
    Solving the Heat Equation in Python \\
    That's it so far.

    \sectionsep

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     COLUMN TWO
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     EXPERIENCE
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Work Experience}

    \runsubsection{DEKA Research And Development}
    \descript{| Software Engineer }
    \location{ Feb. 2017 - Present | Manchester, NH}
    \vspace{\topsep} % Hacky fix for awkward extra vertical space
    \begin{tightemize}
    \item Medical Devices
    \item Linux/DBus/Bluez5/Android8/Bluetooth
    \item Researched and wrote elliptic curve encryption code
    \item Concurrent, resource contrained SQL library in C++
    \item Extensive unittesting and documentation following government requirements
    \end{tightemize}
    \sectionsep

    \runsubsection{freelancer}
    \descript{| Software Engineer }
    \location{ Jul. 2018 - Present | Remote}
    \begin{tightemize}
    \item C++ / GPGPU / Python / Linux. Occasional web front end.
    \end{tightemize}
    \sectionsep

    \runsubsection{Avlino}
    \descript{| Data Scientist }
    \location{Sep. 2015 - Feb. 2017 | Holmdel, NJ}
    \begin{tightemize}
    \item Researched algorithms, implemented in C++, Python and Spark
    \item Read and tweaked open source libraries to suit our needs
    \item Maintained hadoop cluster
    \item Produced business value from tera bytes of social media data
    \item Lead a team of junior devs. in software best practices
    \end{tightemize}
    \sectionsep

    \runsubsection{Battelle}
    \descript{| Modeller }
    \location{Jan. 2015 – Sep. 2015 | Columbus, OH }
    \begin{tightemize}
    \item Wrote and maintained terrorist risk analysis software in R, C++ and Excel VBA
    \item Database maintenance.
    \end{tightemize}
    \sectionsep

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     RESEARCH
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Research}
    \runsubsection{The Sotomayor Lab}
    \descript{| Research Assistant}
    \location{ Jun. 2013 - Jul. 2015 | Columbus, OH}
    Researched epithelial tissues. C++/Python/Linux/Differential Equations/Geometry to model tissue morphogenesis.
    \sectionsep

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     Other Activities
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Recent Projects \& Activities}

    \runsubsection{Manchester Makerspace}
    \descript{| Class Teacher, Maker}
    Teach Arduino Classes. Robotics \& Automotive Projects.
    \sectionsep

    \runsubsection{MathTestMaker}
    \descript{| Founder }
    Full stack. Code procedural math exam content creation, pdf output, and automated grading.
    \sectionsep

    \runsubsection{Color Player Piano}
    \descript{| Maker }
    Made a piano that plays music by reading colors.
    \sectionsep

    \runsubsection{Swing Bot}
    \descript{| Maker }
    Made a robot that swings. Uses an Arduino, accelerometer, servos, and swings like a child. Communicates over I2C.
    \sectionsep

    \runsubsection{Bluetooth}
    \descript{|Hobby}
    I love working with Bluetooth. I've worked with Bluetooth in Linux on the DBus, on the Arduino and in Android. Currently integrating Bluetooth into an open source game engine.

\end{minipage} 
\end{document} 
